\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

% using zitemize instead of itemize will allow for tighter spacing before and after each line

\subsection{{Senior Software Engineer \hfill 03/2023 - present}}
\subtext{DocuSign, Inc. \hfill Seattle, WA}
\vspace*{3pt}
Tasked with delivering frontend for a new docusign product named Maestro and improving developer experience and devops architecture for it.
\begin{zitemize}
\item Delivering frontend for Maestro and facilitating development by adapting an Azure DevOps CI/CD pipeline for monorepo style development
\item Actively identifying and improving developer experience on Maestro repository
\item Augmenting the in-house micro frontend development and deployment system by implementing a feature to allow for monorepo style development
\item Design, implement and execute multiple platform features for the frontend architecture of all teams in Docusign
\end{zitemize}

\vspace*{6pt}

\subsection{{Software Development Engineer II \hfill 11/2019 - 02/2023}}
\subtext{Microsoft Corporation \hfill Bellevue, WA}
\vspace*{3pt}
Promoted to SDE II in the same organization working towards a more senior role. Responsible for projects on front-line worker scenarios in Teams, Visits analytics on Teams Admin Center, and a few addon surfaces in M365 admin center.
\begin{zitemize}
\item Assisted and designed unified engineering efforts - authored a few common npm packages, worked on adopting Module Federation,
\item Conducted a few learning sessions on webpack, Yarn 2, Custom tools authored for reuse, and working sessions to help solidify engineering knowledge in the team
\item Guiding several teams in migrating from an older tech-stack to a newer stack for frontend development.
\item Recently involved more in designing solutions for upcoming projects and infrastructure/engineering improvements.
\end{zitemize}

\vspace*{6pt}

\subsection{{Software Development Engineer I \hfill 09/2018 - 11/2019}}
\subtext{Microsoft Corporation \hfill Bellevue, WA}
\vspace*{3pt}
Responsible to deliver frontend for projects on M365, Teams, Teams EHR connector, and other Small-medium business focused Teams solutions.
\begin{zitemize}
\item Worked with Redux and React on M365 to deliver a setup wizard for Admins
\item Helped build a standalone application that connects EPIC systems with Teams - from development to infrastructure.
\item Set up a basis for a few setup wizards in Teams Admin Center portal.
\end{zitemize}

\vspace*{6pt}

\subsection{{Contractor - Javascript UI Developer \hfill 08/2016 - 07/2018}}
\subtext{CVS Health, through Sapphire IT Services \hfill Florham Park, NJ}
Responsible for delivering UI around caregiver scenarios within CVS Pharmacy website.
\vspace*{3pt}
\begin{zitemize}
\item Migrating angular 1.x code to angular 2 + TypeScript.
\item Developed and maintained a RequireJS based solution to automatically generate dependency configuration (pre-webpack solution)
\item Leading and coordinating with an off-shore team to achieve the goals of CareGiver project.
\end{zitemize}

\vspace*{6pt}

\subsection{{Contractor - PHP and JavaScript Developer \hfill 11/2015 - 06/2016}}
\subtext{Heartland Payment Systems (now Global Payments), through Sapphire IT Services \hfill Plano, TX}
Responsible for a Cordova (web) based mobile application for restaurant payments, and a PHP based service powering it.
\vspace*{3pt}
\begin{zitemize}
\item React-native with Angular 2 explorations for the mobile app
\item Adding features to, and maintaining the PHP based solution + migration from PHP 5 to 7 (purely functional to Class based approach)
\end{zitemize}

\vspace*{6pt}

\subsection{{Graduate Teaching Assistant \hfill 01/2014 - 05/2015}}
\subtext{Missouri S\&T \hfill Rolla, MO}
I was the lab coordinator for Digital Signal Processing and Analog Signals labs for 3 semesters.
\vspace*{3pt}
\begin{zitemize}
\item I taught students how to code in Matlab and how to simulate signals in it.
\item I was also conducting experiments that involve statistical and transform domain properties for real world signals.
\end{zitemize}

\vspace*{6pt}

\subsection{{Contractor - Frontend Developer \hfill 07/2013 - 04/2014}}
\subtext{GXS - through Cachy Graphics \hfill Bangalore, KA, India}
I founded a startup, Cachy Graphics, and along with a partner we delivered software to Nestle through GXS technologies.
\vspace*{3pt}
\begin{zitemize}
\item Worked on an internal project portal on-and-off as a contractor supporting previous projects on defects
\item Designed and delivered an application for warehouse distributors for Nestle - using Cordova
\end{zitemize}

\vspace*{6pt}

\subsection{{Software Engineer - Frontend \hfill 09/2012 - 06/2013}}
\subtext{EzSwype Business Solutions \hfill Bangalore, KA, India}
I was one of the two frontend engineers on the team for this stattup providing guidance and setting up initial development for the website and cordova based mobile app for their payment systems.
\vspace*{3pt}
\begin{zitemize}
\item Branding and Logo design for the company, the website, and Mobile application
\item Set up initial architecture and infrastructure for the website and mobile application.
\end{zitemize}
\end{document}
